\documentclass{article}
\usepackage{times}
\usepackage[small,compact]{titlesec}
\usepackage{textcomp}
\usepackage{url}
\usepackage{hyperref}
\nofiles

\newenvironment{tightitemize}
{\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}
{\end{itemize}}

\begin{document}
{\noindent}\small{\textbf{Theofilos Augoustis
\href{mailto:theofilos.augoustis@gmail.com}{\nolinkurl{<theofilos.augoustis@gmail.com>}}}}

\nointerlineskip
\moveleft\hoffset\vbox{\hrule width\textwidth}
\nointerlineskip

\pagestyle{empty}

\subsection*{Open Source}
I passionately believe in the many societal benefits of open source, and
actively try to get involved with Open Source projects.

\subsection*{Employment and Education}
\begin{tightitemize}

\item \textbf{2018/07--now: Software Engineer, Intel (Timisoara, Romania)}
\begin{tightitemize}
    \item Worked in the Movidius Application Engineering team, as part of the
        Internet-Of-Things Group (IOTG)
    \item Developed significantly Intel's VPU (Visual Processing Unit) Abstraction Layer
        framework that provides RPC-over-USB for OpenCV VPU support.
    \item Worked on the firmware implementation of the Microsoft Azure E2E edge AI
        VPU project.
    \item Customer Neural Network enablement in OpenVINO (UNet, Faster-RCNN).
    \item Developed a configurable power manager for the VPU Neural Network runtime
        engine.
    \item Supported Intel teams in implementing power-efficient VPU configurations.
    \item Implemented an End-to-End testing framework based on GTest for the
        VPU, complete with automatic boot-reset and a comprehensive testing
        suite.
\end{tightitemize}

\bigskip

\item \textbf{2020/12--2021/02: Teaching Assistant, UPT Faculty of Automation
    and Computers (Timisoara, Romania)}
\begin{tightitemize}
\item Recitations with \textasciitilde15 students, plus one-on-one meetings and
    grading of projects. Projects held:
\begin{tightitemize}
    \item ``Interrupt Handling on x86'' (Exploration of Linux's set up of x86
        interrupts (IDT, APIC) and architecture independent handling).
    \item ``Timer Handling on x86'' (Exploration of timer counters on x86 (TSC,
        HPET, PIC) and algorithms for accurate time measurement on Linux).
    \item ``Rowhammer Exploration'' (Exploration of the Rowhammer vulnerability,
        along with possible attack vectors and solutions through a study of
            academic literature on the subject).
\end{tightitemize}
\item Held an interactive x86 assembly programming session, discussing
    instructions, register usage and the SystemV AMD64 ABI.
\end{tightitemize}

\bigskip

\item \textbf{2017/07--2021/07: Polytehnica University of Timisoara,
Bachelor of Engineering in Computer Engineering and Information Technology}
\begin{tightitemize}
\item Developed a working C compiler, including lexing, parsing and code
    generation.
\item Developed a MIPS-compatible processor, complete with full ISA support and
    a FPGA implementation.
\item Participated in the Bitdefender Liga AC LABS programme, focused on x86
    reverse engineering.
\item Participated in the Intel Movidius Liga AC LABS programme, focused on
    Computer Vision fundamentals and vectorized implementations of filters.
\end{tightitemize}
\end{tightitemize}

\bigskip

\subsection*{Interests}
\begin{tightitemize}
    \item Operating System design
    \item Compilers and Optimization
    \item Automata theory
    \item Complexity theory
    \item Computer Architecture
    \item ISAs and microprocessor design
    \item FPGA systems
\end{tightitemize}

\vbox{\hrule width\textwidth}
\begin{tightitemize}
\item\textbf{Operating Systems:} Linux (4 years), Windows NT (1 year).
\item\textbf{Languages (professional---minimum 2 years of active use):} C, C++,
    Python.
\item\textbf{Languages (amateur---minimum 1 extensive project):} x86 assembly,
    MIPS assembly, Java, Scheme, Verilog.
\item\textbf{Technologies:} GCC, LLVM, Pthreads, \LaTeX, SSH, GDB, LLDB,
    valgrind, IDAPro, Git, KVM/QEMU, Xilinx Vivado.
\end{tightitemize}
\vbox{\hrule width\textwidth}

\vfill
\tiny
\center{Last updated \today. 
\LaTeX\ source is available at \href{https://github.com/taugoust/cv-resume}{GitHub}.\\
Copyright \textcopyright\ 2021 Theofilos Augoustis. All rights reserved. Distributed under the \href{http://creativecommons.org/licenses/by-sa/3.0/}{Creative Commons Attribution-ShareAlike 3.0} license.}

\end{document}

